### 2024-11-23 paper.tex
typos

One of the emergent features in UniswapV3 is that you can use concentrated
liquidity positions as limit orders, with the problem that, due to their
logarithmic nature, as prices grow, tick precision decreases. To give
an example, if the current price of bitcoin was 80000USDC, the difference
between the 2 closest ticks is of almost 8USDC. For this reaon, Osmosis introduces
geometric tick spacing with additive ranges \cite{osmosis-price-function}, that
allows to define an order book on top of the AMM with proper tick precision.
Then, its easy to verify that Osmosis price function is:
\[
\rho(t) = 10^{\lfloor t/9e6\rfloor - 6} \left(
    t - 10^6\left(9\left\lfloor\frac{t}{9e6}\right\rfloor - 1\right)
\right)
\]

@@

around the new current price. Moreover, its easy to see that the total vault reserves

@@

proportion, but its still theoretically possible a vault could get rebalanced

@@

        feel like. Thus, its up to the admin to decide the rebalancing strategy off-chain.

@@

\section{Price function inverse}
The only missing piece is the generalized inverse $\rho^{-1}$ that will let
us map every price to its closest tick in Osmosis. We will prove that such
function is:
\[
\rho^{-1}(p) = 10^{6-\lfloor\log p\rfloor} \left(
	p+10^{\lfloor\log p\rfloor}\left(
		9\lfloor\log p\rfloor-1
	\right)
\right)
\]
Of course, it could be the case that there was 2 different prices with the same
tick, as we require ticks to be integers (ie, we will take $\rho^{-1}(p) :=
\lfloor \rho^{-1}(p)\rfloor$). Moreover, there could be 2 ticks that map to the
same price, due to computational precision. Thats why by generalized inverse we
mean 2 things:
\begin{enumerate}
    \item Generalized inverse property: $\forall t\in T: \rho^{-1}(\rho(t)) =
        t$, where $T\subset\mathbb Z$ is the tick space.
    \item Closeness property: $\forall t_0, t_1\in T$ s.t. $t_1 > t_0$, we have
        that $\forall p\in [\rho(t_0), \rho(t_1)]$ its the case that
        $\rho^{-1}(p)\in[t_0, t_1]$. That is, given any 2 ticks, if we map them
        to the price space and pick any price in that range, that price tick will
        also be in the tick range after pulling it back.
\end{enumerate}
But its easy to check that the weaker form of the closeness property when $t_1
= t_0 + 1$ is equivalent to the general form. The generalized inverse property
is not enough for our usecase, as we just mentioned there will be prices that
map to the same tick. Informally, by proving the weak closeness
property, we will know that any price will get mapped to its closest tick or
its second closes tick (which, for our usecase, is good enough). The proof
sketch goes as follows:
\begin{enumerate}
    \item Prove the generalized inverse property by simple brute force (as the
        domain is finite and relativelly small).
    \item Observe both $\rho^{-1}$ and $\rho$ are monotone non-decreasing.
    \item Conclued trivially that the weak closeness property holds, by simply
        taking inverses over $\rho(t_0) \leq p \leq \rho(t_0 + 1)$.
\end{enumerate}

>>>>

One of the emergent features in UniswapV3 is that you can use concentrated
liquidity positions as limit orders, with the problem that, due to their
logarithmic nature, as prices grow, tick precision decreases. To give
an example, if the current price of bitcoin was 80000USDC, the difference
between the 2 closest ticks is of almost 8USDC. For this reaon, Osmosis introduces
geometric tick spacing with additive ranges \cite{osmosis-price-function}, that
allows to define an order book on top of the AMM with proper tick precision.
Then, it's easy to verify that Osmosis price function is:
\[
\rho(t) = 10^{\lfloor t/9e6\rfloor - 6} \left(
    t - 10^6\left(9\left\lfloor\frac{t}{9e6}\right\rfloor - 1\right)
\right)
\]

@@

around the new current price. Moreover, it's easy to see that the total vault reserves

@@

proportion, but it's still theoretically possible a vault could get rebalanced

@@

        feel like. Thus, it's up to the admin to decide the rebalancing strategy off-chain.

@@

\section{Price function inverse}
The only missing piece is the generalized inverse $\rho^{-1}$ that will let
us map every price to its closest tick in Osmosis. We will prove that such
function is:
\[
\rho^{-1}(p) = 10^{6-\lfloor\log p\rfloor} \left(
	p+10^{\lfloor\log p\rfloor}\left(
		9\lfloor\log p\rfloor-1
	\right)
\right)
\]
Of course, it could be the case that there was 2 different prices with the same
tick, as we require ticks to be integers (ie, we will take $\rho^{-1}(p) :=
\lfloor \rho^{-1}(p)\rfloor$). Moreover, there could be 2 ticks that map to the
same price, due to computational precision. Thats why by generalized inverse we
mean 2 things:
\begin{enumerate}
    \item Generalized inverse property: $\forall t\in T: \rho^{-1}(\rho(t)) =
        t$, where $T\subset\mathbb Z$ is the tick space.
    \item Closeness property: $\forall t_0, t_1\in T$ s.t. $t_1 > t_0$, we have
        that $\forall p\in [\rho(t_0), \rho(t_1)]$ it's the case that
        $\rho^{-1}(p)\in[t_0, t_1]$. That is, given any 2 ticks, if we map them
        to the price space and pick any price in that range, that price tick will
        also be in the tick range after pulling it back.
\end{enumerate}
But it's easy to check that the weaker form of the closeness property when $t_1
= t_0 + 1$ is equivalent to the general form. The generalized inverse property
is not enough for our usecase, as we just mentioned there will be prices that
map to the same tick. Informally, by proving the weak closeness
property, we will know that any price will get mapped to its closest tick or
its second closes tick (which, for our usecase, is good enough). The proof
sketch goes as follows:
\begin{enumerate}
    \item Prove the generalized inverse property by simple brute force (as the
        domain is finite and relativelly small).
    \item Observe both $\rho^{-1}$ and $\rho$ are monotone non-decreasing.
    \item Conclued trivially that the weak closeness property holds, by simply
        taking inverses over $\rho(t_0) \leq p \leq \rho(t_0 + 1)$.
\end{enumerate}
